---
title: "Untitled"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(data.table)
library(dplyr)
setwd("~/Desktop/Columbia University/third semester/Applied Data Science/project 1/dataset")
# FData1 = fread("ss14husa.csv",select = c("TEN","NP","ST"))
# FData2 = fread("ss14husb.csv",select=c("TEN","NP","ST"))
# FData = rbind(FData1,FData2)
# rm(FData1,FData2)
# save(FData,file = "F1.RData")
load("F1.RData")


```
```{r}
GetD<-function(x){
  Rent = FData%>%filter(TEN == 3)
Buy = FData%>%filter(TEN == c(1,2))
N_NY.Rent = FData%>%filter(!is.na(NP))%>%select(NP,TEN,ST)%>%mutate(NP=as.numeric(NP))%>%
  filter(ST == as.character(x))%>%select(NP,TEN)%>%group_by(NP)%>%summarise(Percentage = n())%>%mutate(Percentage = Percentage/sum(Percentage))%>%mutate(TEN = "RENT")

N_NY.Buy = Buy%>%filter(!is.na(NP))%>%select(NP,TEN,ST)%>%mutate(NP=as.numeric(NP))%>%
  filter(ST == as.character(x))%>%select(NP,TEN)%>%group_by(NP)%>%summarise(Percentage = n())%>%mutate(Percentage = Percentage/sum(Percentage))%>%mutate(TEN = "BUY")
         
N_NY.Rent.Buy = rbind(N_NY.Rent,N_NY.Buy)
return(N_NY.Rent.Buy)
}
```



```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("State", label = "StateCode",
              choices = 1:40, selected = 5)
)
renderPlot({
  ggplot(GetD(input$State),aes(x = NP, y = Percentage, width = 0.7, fill = TEN)) + geom_bar(stat = "identity",  position = "dodge")+
  ggtitle("Number of People in the House in New York") + labs(x = "Number of people",y="Percentage") 
  
})
```



## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



